I would like to thank my parents for the unparallelled support and encouragement they
have provided over the years, as well as in the year in which this work was carried out.
I wouldn't be here without their words of affection and wisdom, and I cannot thank them
enough.\\
I would also like to thank Dr. R. Lekshmi for the ceaseless guidance and for the keen
insight into the problems faced along the way. With her ready assistance and patience
carrying out this project, even if remotely, was engaging and rewarding.\\
Additionally, I would like to thank Dr. K. G. Arun at the Chennai Mathematical Institute
in Tamilnadu, India and Dr. M. Saleem at the University of Minnesota in Minneapolis,
United States for their contributions and for guidance in this work. I would also like
to thank Dr. B. S. Sathyaprakash, at the Pennsylvania State University, University Park,
United States for his invaluable inputs and constructive remarks on the arguments
developed here, which greatly helped to structure and refine this work.\\
In addition, I would also like to thank the support staff at IIST, especially Mr. Sai
Krishnan at the Astronomy Lab, who has helped greatly specially in the setup and
maintenance of the remote access node to workstations at IIST.\\
I would also like to thank Ms. Aashka Oza for her excellent suggestions which helped
improve the presentation and the flow of this report greatly. Additionally, I would like
to thank her for the tremendous support and inspiration that she has given me during the
entire course of my time at IIST. My life has been richer with her amazing \emph{joie
de vivre} and infallible companionship.\\
Furthermore, I would also like to acknowledge the tremendous contributions of the libre
and open source community via their core utilities and tools. Without the natural
suitability of these tools for scientific workflows and excellent text editing support
of Vim, this body of work would have been an unnecessarily herculean task.\\
Finally, I would like to acknowledge the immense efforts of those who have risked
their lives during such unprecedented times for the benefit of others, and to ensure
that essential services and societal infrastructures still operate.

\vspace{8mm}
\hfill \Author \hspace{5mm}
